### 2009-08-26 latex/paper1/contents.tex
paper1

\section{Software Networks}

@@

@@

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

All models produce networks that resemble software networks.

For some parameters, though, the networks are not realistic.

We cannot blame one single parameter for the non-realism.

@@

>>>>

\section{Software Networks and Software Clustering}

@@

Glossary: preferential attachment

\subsection{ER (Erdos-Renyi)}

@@

TODO: Argument: why the imposed modules are natural modules?

@@

\subsection{Software Network Extraction}

@@

\subsection{Oracle Training and Evaluation}

@@

\subsection{Network Synthesis}

In assessing the realism of a model, we want to know if, with a proper choice of
parameters, the model is capable of producing a realistic network. In order to
do so, we must generate many networks using different combinations of
parameters.

Since most of the parameters can assume infinite distinct values, we chose to
fix some of them and vary the others in discrete steps. In all models the number
of vertices was fixed to 1000. We generated one network for each set of
parameters. Here we describe the criteria we use to choose the parameters for
each model.

\subsubsection{BCR+}

We chose five different module dependency networks, which where extracted from
actual dependencies between modules of five different software systems of our
sample, ranging from 2 to 32 modules. The module dependency networks are shown
on Figure XXX.

The probabilities p, q and r were given all possible values from 0.0 upto 1.0,
in 0.2 steps, such as the sum of the probabilities was 1. Since the only events
that create vertices are those associated with probabilities p and q, we imposed
the additional restriction that p + q > 0.

For deltain and deltaout we assigned the integer numbers from 0 to 4. TODO: why

Finally, we chose mu from 0.0 to 0.6 in 0.2 steps. It does not make sense to
choose higher values since they mean that there will be more edges connecting
different models.

%02-gef
%04-ibatis
%08-megamek
%16-findbugs
%32-zk

In order to asses the realism of the models we should test them with

In order to assess the realism of the models, we generated a large number of
networks using the models with many combinations of parameters.

We expect that,
if a model is capable of producing a realistic network, then

@@

ER: ...

@@

Table: Model | Number of Networks | Realistic Networks | \%

Show some graphs: histogram of average correlations for each model.

As expected, ER produces non-realistic software networks.

All models produce networks that resemble software networks.  For some
parameters, though, the networks are not realistic.

\subsection{Patterns in Parameters}

1R

Naive Bayes

\subsection{Homogeinity}

Pick realistic networks from a model. Are they similar to each other? (see
standard deviation) Are they similar to networks generated by the other models?

\section{Threads to validity}

% External validity (EV): can it be generalized?
Structural information isn't enough for a expert do produce a
decomposition (s/he may use data such as names and external documentation).

Even when considering only structural information, is it true
that experts would find a decomposition similar to the reference decomposition
imposed by the model?

We generated only one network for each set of parameters.

Some clustering algorithms use weights and they weren't studied here.

EV: We've only studied 65 systems, which is not that much.

We only studied object-oriented systems implemented in Java. Maybe the results
would be different if we studied systems implement in other languagens or using
other paradigms. The choice of a particular technique for extracting
dependencies (static analysis) may also have impact on the structure of the
networks.

# Koschke says that experts decompositions vary by no more than 80? percent.

@@

\section{Appendix A: list of networks}

Software networks:

Name | Source

Other networks:

Description | Source
